### 2015-11-13 ch02-qlogms/excitation-design.tex
Quite some work on ch02

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$ 
       & $\round{\frac{\alpha f_k}{\Delta f}} \Delta f$\\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & \ldots\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}

    \TODO{afmaken}
  \end{table}

@@

\section{Optimization of the frequency spacing} \label{sec:optimAlpha}
  \subsection{Calculation of the model uncertainty}
  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing factor $\alpha$, has not been designed for.
  In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the Cramér-Rao Lower Bound.
  Doing so will allow to determine a suitable value for the frequency spacing $\alpha$.

>>>>

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\leq \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\leq \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}
  \TODO{tabel: verschillende signalen: power per BW}

@@

\section{Optimization of the frequency spacing} \label{sec:optimAlpha}
  \subsection{Calculation of the model uncertainty}
  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing $\alpha$, has not been designed.

  In this section we show a possible approach to compare the performance of different excitation signals with respect to the theoretically minimal attainable uncertainty of the transfer function as expressed by the Cramér-Rao Lower Bound.
  Doing so allows to determine a suitable value for the frequency spacing $\alpha$.

### 2015-11-13 ch02-qlogms/sysid.tex
Quite some work on ch02

Direct calculations for $\damping < 1$ give
\begin{align}
\label{eq:auto}
\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
\end{align}
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
% \begin{align}
% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:cross1} \\
% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:cross}
% \end{align}
\begin{gather}
\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:cross1} \\
\leq
\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \wn[1]} &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}{\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in Fig.~\ref{fig:dG}.

@@

In Fig.~\ref{fig:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling. The diagonal blocks of the normalized $\IF$ in all cases have some elements close to 1. In this example, the $\damping$ is set to be the same in both sub-systems. Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.

>>>>

Direct calculations for $\damping < 1$ give
\begin{align}
\label{eq:auto}
\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
\end{align}
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
% \begin{align}
% &\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right| \leq\label{eq:cross1} \\
% &\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega \leq \\
% &\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega.\label{eq:cross}
% \end{align}
\begin{gather}
\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:cross1} \\
\leq
\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \wn[1]} &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}{\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:dG}.

@@

In \figref{fig:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well separated increases the decoupling. The diagonal blocks of the normalized $\IF$ in all cases have some elements close to 1. In this example, the $\damping$ is set to be the same in both sub-systems. Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.
